---
title: "Assessment of TRMM vs PACRAIN raw data conditioned to Weather Types"
author: "Óscar Mirones Alonso"
output: 
  html_notebook:
    theme: united
    toc: yes
    toc_depth: 5
---

# Preview

In this part everything necessary prior to the analysis is collected. The libraries are loaded, the data and some function necessary for the calculation of some validation index is implemented.

First, libraries are loaded
```{r eval=TRUE, message=FALSE}
library(loadeR)
library(transformeR)
library(downscaleR)
library(visualizeR)
library(convertR)
library(ncdf4)
library(climate4R.value)
library(magrittr)
library(evd)
library(formattable) #neccessary to create tables with colors
library(lubridate) #neccessary to calculate differences in years between dates
```

```{r}
if (dir.exists("C:/Users/usuario/Desktop/TRMM-Calibration/Data")) {
  dir <- "C:/Users/usuario/Desktop/TRMM-Calibration/Data"
}else{
  dir <- "/vols/seal/oceano/gmeteo/WORK/juaco/trmm/clustering"
}
```

```{r setup}
knitr::opts_knit$set(root.dir = dir)
```

```{r}
set.seed(42)
```


PCA data from other notebook is loaded.
```{r}
load("pca.RData")
```

Reanalysis data is loaded to compute later the spatialPlot of the clusters.
```{r}
load("pp_reanalysis.RData")

```


Here a subsetting is made with the goal of restrict the number of PCs involved (since PCs'number related with precipitation is over 2000). So, the variance explained is 0.75,0.9 and 0.9 for precipitation, sea level pressure and difference sea level pressure respectively. 
```{r}
idx.tp <- which(attributes(pca$tp[[1]])$explained_variance >= .75)[1]
idx.msl <- which(attributes(pca$msl[[1]])$explained_variance >= .9)[1]
idx.diff.msl <- which(attributes(pca$diff_msl[[1]])$explained_variance >= .9)[1]

pca.matrix <- cbind(pca$tp[[1]]$PCs[,1:idx.tp],pca$msl[[1]]$PCs[,1:idx.msl],pca$diff_msl[[1]]$PCs[,1:idx.diff.msl])

```


It is good to preview the intracluster error against the number of clusters computed. The selection made is k=5 and k=6.
```{r}
totWithinss <- c(1:15)

for(i in 1:15){
  kmModel<- kmeans(pca.matrix, centers = i, nstart = 1)
  totWithinss[i]<- kmModel$tot.withinss

}
plot(x=1:15,y=totWithinss,type="b", xlab="N. Of Cluster",ylab="Within groups sum of squares")
```



So, the kmeans model is computed and saved for the optimum k.
```{r}
k = 5
kmModel5 <- kmeans(pca.matrix, centers = k, nstart = 10)
summary(kmModel5)
```
Station locations are plotted with their corresponding codes.
```{r}
if (dir =="/vols/seal/oceano/gmeteo/WORK/juaco/trmm/clustering" ) {
  stationInfo("/SP_ascii.zip")
}else{
  stationInfo("C:/Users/usuario/Desktop/TRMM-Calibration/TRMM-time-series/WT_Analysis_Calibration/SP_ascii.zip")
}

```


```{r}
lista <- lapply(1:k, function(x) subsetDimension(pp_reanalysis, dimension = "time", indices = which(kmModel5$cluster == x)) %>% climatology())

kmedias.pp <- bindGrid(lista, dimension = "member", skip.temporal.check = TRUE)

spatialPlot(kmedias.pp,backdrop.theme = 'countries', rev.color = T, as.table = T, names.attr = paste("Days in cluster", 1:k, ":",kmModel5$size[1:k]))
```


```{r}
k = 6
kmModel6 <- kmeans(pca.matrix, centers = k, nstart = 10)
summary(kmModel6)
```
```{r}
lista <- lapply(1:k, function(x) subsetDimension(pp_reanalysis, dimension = "time", indices = which(kmModel6$cluster == x)) %>% climatology())

kmedias.pp <- bindGrid(lista, dimension = "member", skip.temporal.check = TRUE)

spatialPlot(kmedias.pp,backdrop.theme = 'countries', rev.color = T, as.table = T, names.attr = paste("Days in cluster", 1:k, ":",kmModel6$size[1:k]))
```

MaxReturnValue function is computed to calculate the Maximum Return Value in 20 years index.
```{r}
MaxReturnValue <- function(data){
  #library(lubridate)
  #nyears <- round(time_length(difftime(cal.madrid.eqm$Dates$end[length(cal.madrid.eqm$Dates$end)], cal.madrid.eqm$Dates$start[1]),"years"))
  nyears <- 20
  data.maxYear <- aggregateGrid(redim(data), aggr.y = list(FUN = "max",na.rm = TRUE))

  data.maxrv <- climatology(data, clim.fun = list(FUN = "mean", na.rm = T))

  auxData <- data.maxYear$Data
  auxData[which(is.infinite(auxData))] <- NA

  if (any(!is.na(auxData))){
      auxGEV <- fgev(auxData)
      if ((auxGEV$estimate[3] - auxGEV$std.err[3] < 0) & (0  < auxGEV$estimate[3] + auxGEV$std.err[3])){
        auxGEV <- fgev(auxData, shape = 0)
        auxRV <- qgev(1-1/nyears, loc = auxGEV$estimate[1], scale = auxGEV$estimate[2], shape = 0)
      }else{
        auxRV <- qgev(1-1/nyears, loc = auxGEV$estimate[1], scale = auxGEV$estimate[2], shape = auxGEV$estimate[3])
      }
      data.maxrv <- as.numeric(auxRV)
      names(data.maxrv) <- paste("RV",nyears,"_max", sep = "")
  }
  return(data.maxrv)
  }
```



Finally, PACRAIN and TRMM precipitation data is loaded using loadeR funciton loadStationData. This data readout is easy and fast since both datasets are established in a ASCII format for each of the 7 PACRAIN station existing in our target area. Obviously, precip_obs is related with PACRAIN data and precip_trmm with TRMM data.

```{r}
if (dir =="/vols/seal/oceano/gmeteo/WORK/juaco/trmm/clustering" ) {
  precip_obs <- loadStationData("SP_ascii.zip", var = "precip_obs")
}else{
  precip_obs <- loadStationData("C:/Users/usuario/Desktop/TRMM-Calibration/TRMM-time-series/WT_Analysis_Calibration/SP_ascii.zip", var = "precip_obs")
}


```

```{r}
if (dir =="/vols/seal/oceano/gmeteo/WORK/juaco/trmm/clustering" ) {
  precip_trmm <- loadStationData("SP_ascii.zip", var = "precip_trmm")
}else{
  precip_trmm <- loadStationData("C:/Users/usuario/Desktop/TRMM-Calibration/TRMM-time-series/WT_Analysis_Calibration/SP_ascii.zip", var = "precip_trmm")
}


```
# Assessment in PACRAIN stations

## Kolopelu (Wallis and Futuna) Station

### Raw not conditioned data

Target station data(TRMM and PACRAIN) selection.
```{r}
i=1

station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])
```



```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
# temporalPlot(station.obs,station.reanalysis, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```

```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

# index.reanalysis <- valueIndex1D(station.reanalysis$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
# index.reanalysis.rv20max <- MaxReturnValue(station.reanalysis)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
# index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r}
df <- data.frame(index.obs,index.trmm)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

### Assessment conditioned on WT

#### k=5

```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

#### k = 6
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 5))
station.obs.cl6 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 5))
station.trmm.cl6 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl6 <- valueIndex1D(station.obs.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl6 <- c(index.obs.cl6, valueIndex1D(station.obs.cl6$Data[!is.na(station.obs.cl6$Data)], index.codes = "P98WetAmount"))
index.obs.cl6.rv20max <- MaxReturnValue(station.obs.cl6)

index.trmm.cl6 <- valueIndex1D(station.trmm.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl6 <- c(index.trmm.cl6, valueIndex1D(station.trmm.cl6$Data[!is.na(station.trmm.cl6$Data)], index.codes = "P98WetAmount"))
index.trmm.cl6.rv20max <- MaxReturnValue(station.trmm.cl6)
```

```{r}
index.obs.cl6 <- c(index.obs.cl6, index.obs.cl6.rv20max)
index.trmm.cl6 <- c(index.trmm.cl6, index.trmm.cl6.rv20max)
```

##### Index assessment conditioned on WT6
```{r}
df <- data.frame(index.obs.cl6,index.trmm.cl6)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5),abs(index.trmm.cl6-index.obs.cl6)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5","WT6")

format(diff.df, digits = 3, scientific = 5)
```

## Hakupu (Niue) station

### Raw not conditioned data
```{r}
i=2

station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])
```

```{r}
# idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
#  
# lon <- pp_reanalysis$xyCoords$x[idx]
#   
# idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
# lat <- pp_reanalysis$xyCoords$y[idx2]
#   
# station.reanalysis <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)
```


```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
# temporalPlot(station.obs,station.reanalysis, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```


```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

# index.reanalysis <- valueIndex1D(station.reanalysis$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
# index.reanalysis.rv20max <- MaxReturnValue(station.reanalysis)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
# index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r}
df <- data.frame(index.obs,index.trmm)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

### Assessment conditioned on WT

#### k=5
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

#### k = 6
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 5))
station.obs.cl6 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 5))
station.trmm.cl6 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl6 <- valueIndex1D(station.obs.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl6 <- c(index.obs.cl6, valueIndex1D(station.obs.cl6$Data[!is.na(station.obs.cl6$Data)], index.codes = "P98WetAmount"))
index.obs.cl6.rv20max <- MaxReturnValue(station.obs.cl6)

index.trmm.cl6 <- valueIndex1D(station.trmm.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl6 <- c(index.trmm.cl6, valueIndex1D(station.trmm.cl6$Data[!is.na(station.trmm.cl6$Data)], index.codes = "P98WetAmount"))
index.trmm.cl6.rv20max <- MaxReturnValue(station.trmm.cl6)
```

```{r}
index.obs.cl6 <- c(index.obs.cl6, index.obs.cl6.rv20max)
index.trmm.cl6 <- c(index.trmm.cl6, index.trmm.cl6.rv20max)
```

##### Index assessment conditioned on WT6
```{r}
df <- data.frame(index.obs.cl6,index.trmm.cl6)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5),abs(index.trmm.cl6-index.obs.cl6)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5","WT6")

format(diff.df, digits = 3, scientific = 5)
```

## Rarotonga International Airport (Cook Island) station

### Raw not conditioned data
```{r}
i=3

station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])
```

```{r}
# idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
#  
# lon <- pp_reanalysis$xyCoords$x[idx]
#   
# idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
# lat <- pp_reanalysis$xyCoords$y[idx2]
#   
# station.reanalysis <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)
```

```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
# temporalPlot(station.obs,station.reanalysis, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```


```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

# index.reanalysis <- valueIndex1D(station.reanalysis$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
# index.reanalysis.rv20max <- MaxReturnValue(station.reanalysis)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
# index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r}
df <- data.frame(index.obs,index.trmm)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

### Assessment conditioned on WT

#### k=5
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```


#### k = 6
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 5))
station.obs.cl6 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 5))
station.trmm.cl6 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl6 <- valueIndex1D(station.obs.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl6 <- c(index.obs.cl6, valueIndex1D(station.obs.cl6$Data[!is.na(station.obs.cl6$Data)], index.codes = "P98WetAmount"))
index.obs.cl6.rv20max <- MaxReturnValue(station.obs.cl6)

index.trmm.cl6 <- valueIndex1D(station.trmm.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl6 <- c(index.trmm.cl6, valueIndex1D(station.trmm.cl6$Data[!is.na(station.trmm.cl6$Data)], index.codes = "P98WetAmount"))
index.trmm.cl6.rv20max <- MaxReturnValue(station.trmm.cl6)
```

```{r}
index.obs.cl6 <- c(index.obs.cl6, index.obs.cl6.rv20max)
index.trmm.cl6 <- c(index.trmm.cl6, index.trmm.cl6.rv20max)
```

##### Index assessment conditioned on WT6
```{r}
df <- data.frame(index.obs.cl6,index.trmm.cl6)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5),abs(index.trmm.cl6-index.obs.cl6)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5","WT6")

format(diff.df, digits = 3, scientific = 5)
```

## Bells Beach (New Zealand) station

### Raw not conditioned data
```{r}
i=4

station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])
```

```{r}
# idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
#  
# lon <- pp_reanalysis$xyCoords$x[idx]
#   
# idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
# lat <- pp_reanalysis$xyCoords$y[idx2]
#   
# station.reanalysis <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)
```


```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
# temporalPlot(station.obs,station.reanalysis, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```


```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

# index.reanalysis <- valueIndex1D(station.reanalysis$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
# index.reanalysis.rv20max <- MaxReturnValue(station.reanalysis)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
# index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r}
df <- data.frame(index.obs,index.trmm)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

### Assessment conditioned on WT

#### k=5
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

#### k = 6
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 5))
station.obs.cl6 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 5))
station.trmm.cl6 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl6 <- valueIndex1D(station.obs.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl6 <- c(index.obs.cl6, valueIndex1D(station.obs.cl6$Data[!is.na(station.obs.cl6$Data)], index.codes = "P98WetAmount"))
index.obs.cl6.rv20max <- MaxReturnValue(station.obs.cl6)

index.trmm.cl6 <- valueIndex1D(station.trmm.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl6 <- c(index.trmm.cl6, valueIndex1D(station.trmm.cl6$Data[!is.na(station.trmm.cl6$Data)], index.codes = "P98WetAmount"))
index.trmm.cl6.rv20max <- MaxReturnValue(station.trmm.cl6)
```

```{r}
index.obs.cl6 <- c(index.obs.cl6, index.obs.cl6.rv20max)
index.trmm.cl6 <- c(index.trmm.cl6, index.trmm.cl6.rv20max)
```

##### Index assessment conditioned on WT6
```{r}
df <- data.frame(index.obs.cl6,index.trmm.cl6)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5),abs(index.trmm.cl6-index.obs.cl6)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5","WT6")

format(diff.df, digits = 3, scientific = 5)
```

## Possible ocean buoy

### Raw not conditioned data
```{r}
i=5

station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])
```

```{r}
# idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
#  
# lon <- pp_reanalysis$xyCoords$x[idx]
#   
# idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
# lat <- pp_reanalysis$xyCoords$y[idx2]
#   
# station.reanalysis <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)
```


```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
# temporalPlot(station.obs,station.reanalysis, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```


```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

# index.reanalysis <- valueIndex1D(station.reanalysis$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
# index.reanalysis.rv20max <- MaxReturnValue(station.reanalysis)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
# index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r}
df <- data.frame(index.obs,index.trmm)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

### Assessment conditioned on WT

#### k=5
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

#### k = 6
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 5))
station.obs.cl6 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 5))
station.trmm.cl6 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl6 <- valueIndex1D(station.obs.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl6 <- c(index.obs.cl6, valueIndex1D(station.obs.cl6$Data[!is.na(station.obs.cl6$Data)], index.codes = "P98WetAmount"))
index.obs.cl6.rv20max <- MaxReturnValue(station.obs.cl6)

index.trmm.cl6 <- valueIndex1D(station.trmm.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl6 <- c(index.trmm.cl6, valueIndex1D(station.trmm.cl6$Data[!is.na(station.trmm.cl6$Data)], index.codes = "P98WetAmount"))
index.trmm.cl6.rv20max <- MaxReturnValue(station.trmm.cl6)
```

```{r}
index.obs.cl6 <- c(index.obs.cl6, index.obs.cl6.rv20max)
index.trmm.cl6 <- c(index.trmm.cl6, index.trmm.cl6.rv20max)
```

##### Index assessment conditioned on WT6
```{r}
df <- data.frame(index.obs.cl6,index.trmm.cl6)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5),abs(index.trmm.cl6-index.obs.cl6)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5","WT6")

format(diff.df, digits = 3, scientific = 5)
```

## Aoloau (American Samoa) station

### Raw not conditioned data
```{r}
i=6

station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])
```

```{r}
# idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
#  
# lon <- pp_reanalysis$xyCoords$x[idx]
#   
# idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
# lat <- pp_reanalysis$xyCoords$y[idx2]
#   
# station.reanalysis <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)
```


```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
# temporalPlot(station.obs,station.reanalysis, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```


```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

# index.reanalysis <- valueIndex1D(station.reanalysis$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
# index.reanalysis.rv20max <- MaxReturnValue(station.reanalysis)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
# index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r}
df <- data.frame(index.obs,index.trmm)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

### Assessment conditioned on WT

#### k=5
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

#### k = 6
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 5))
station.obs.cl6 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 5))
station.trmm.cl6 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl6 <- valueIndex1D(station.obs.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl6 <- c(index.obs.cl6, valueIndex1D(station.obs.cl6$Data[!is.na(station.obs.cl6$Data)], index.codes = "P98WetAmount"))
index.obs.cl6.rv20max <- MaxReturnValue(station.obs.cl6)

index.trmm.cl6 <- valueIndex1D(station.trmm.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl6 <- c(index.trmm.cl6, valueIndex1D(station.trmm.cl6$Data[!is.na(station.trmm.cl6$Data)], index.codes = "P98WetAmount"))
index.trmm.cl6.rv20max <- MaxReturnValue(station.trmm.cl6)
```

```{r}
index.obs.cl6 <- c(index.obs.cl6, index.obs.cl6.rv20max)
index.trmm.cl6 <- c(index.trmm.cl6, index.trmm.cl6.rv20max)
```

##### Index assessment conditioned on WT6
```{r}
df <- data.frame(index.obs.cl6,index.trmm.cl6)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5),abs(index.trmm.cl6-index.obs.cl6)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5","WT6")

format(diff.df, digits = 3, scientific = 5)
```

## Aoloau (American Samoa) station (low elevation)

### Raw not conditioned data
```{r}
i=7

station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])
```

```{r}
# idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
#  
# lon <- pp_reanalysis$xyCoords$x[idx]
#   
# idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
# lat <- pp_reanalysis$xyCoords$y[idx2]
#   
# station.reanalysis <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)
```


```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
# temporalPlot(station.obs,station.reanalysis, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```


```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

# index.reanalysis <- valueIndex1D(station.reanalysis$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
# index.reanalysis.rv20max <- MaxReturnValue(station.reanalysis)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
# index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r}
df <- data.frame(index.obs,index.trmm)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

### Assessment conditioned on WT

#### k=5
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

#### k = 6
```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 5))
station.obs.cl6 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 5))
station.trmm.cl6 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel6$cluster == 6))
```

```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl6 <- valueIndex1D(station.obs.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl6 <- c(index.obs.cl6, valueIndex1D(station.obs.cl6$Data[!is.na(station.obs.cl6$Data)], index.codes = "P98WetAmount"))
index.obs.cl6.rv20max <- MaxReturnValue(station.obs.cl6)

index.trmm.cl6 <- valueIndex1D(station.trmm.cl6$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl6 <- c(index.trmm.cl6, valueIndex1D(station.trmm.cl6$Data[!is.na(station.trmm.cl6$Data)], index.codes = "P98WetAmount"))
index.trmm.cl6.rv20max <- MaxReturnValue(station.trmm.cl6)
```

```{r}
index.obs.cl6 <- c(index.obs.cl6, index.obs.cl6.rv20max)
index.trmm.cl6 <- c(index.trmm.cl6, index.trmm.cl6.rv20max)
```

##### Index assessment conditioned on WT6
```{r}
df <- data.frame(index.obs.cl6,index.trmm.cl6)
colnames(df) <- c("Obs", "TRMM")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5),abs(index.trmm.cl6-index.obs.cl6)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5","WT6")

format(diff.df, digits = 3, scientific = 5)
```


