---
title: "Assessment of TRMM vs PACRAIN raw data conditioned to Weather Types"
author: "Óscar Mirones Alonso"
output: 
  html_notebook:
    theme: united
    toc: yes
    toc_depth: 5
---

```{r}
if (dir.exists("C:/Users/usuario/Desktop/TRMM-Calibration/Data")) {
  dir <- "C:/Users/usuario/Desktop/TRMM-Calibration/Data"
}else{
  dir <- "/vols/seal/oceano/gmeteo/WORK/juaco/trmm"
}

```

```{r setup}
knitr::opts_knit$set(root.dir = dir)
```

```{r check-wd}
getwd()
```
# Preview

In this part everything necessary prior to the analysis is collected. The libraries are loaded, the data and some function necessary for the calculation of some validation index is implemented.

First, libraries are loaded
```{r eval=TRUE, message=FALSE}
library(loadeR)
library(transformeR)
library(downscaleR)
library(visualizeR)
library(convertR)
library(ncdf4)
library(climate4R.value)
library(magrittr)
library(evd)
library(formattable) #neccessary to create tables with colors
library(lubridate) #neccessary to calculate differences in years between dates
library(lattice)
library(ggplot2)
library(raster)
library(rasterVis)
library(sp)
```
```{r}
set.seed(42)
```


PCA data from other notebook is loaded.
```{r}
load("pca.RData")
```

Reanalysis data is loaded to compute later the spatialPlot of the clusters.
```{r}
load("pp_reanalysis.RData")
```




Here a subsetting is made with the goal of restrict the number of PCs involved (since PCs'number related with precipitation is over 2000). So, the variance explained is 0.75,0.9 and 0.9 for precipitation, sea level pressure and difference sea level pressure respectively. 
```{r}
idx.tp <- which(attributes(pca$tp[[1]])$explained_variance >= .75)[1]
idx.msl <- which(attributes(pca$msl[[1]])$explained_variance >= .9)[1]
idx.diff.msl <- which(attributes(pca$diff_msl[[1]])$explained_variance >= .9)[1]

pca.matrix <- cbind(pca$tp[[1]]$PCs[,1:idx.tp],pca$msl[[1]]$PCs[,1:idx.msl],pca$diff_msl[[1]]$PCs[,1:idx.diff.msl])

```


It is good to preview the intracluster error against the number of clusters computed. The selection made is k=5 and k=6.
```{r}
totWithinss <- c(1:15)

for(i in 1:15){
  kmModel<- kmeans(pca.matrix, centers = i, nstart = 1)
  totWithinss[i]<- kmModel$tot.withinss

}
plot(x=1:15,y=totWithinss,type="b", xlab="N. Of Cluster",ylab="Within groups sum of squares")
```



So, the kmeans model is computed and saved for the optimum k.
```{r}
k = 5
kmModel5 <- kmeans(pca.matrix, centers = k, nstart = 10)
summary(kmModel5)
```
Station locations are plotted with their corresponding codes.
```{r}
stationInfo("SP_ascii.zip")
```
```{r}
cyclones <- read.csv('C:/Users/usuario/Desktop/Master/tfm/Notebooks_TFM/SP_cyclones_time_series_1998_2020.csv')
cyclones$Date <- as.Date(cyclones$Date)
cyclones <- cyclones[,2:3]

```


```{r}
lista <- lapply(1:k, function(x) subsetDimension(pp_reanalysis, dimension = "time", indices = which(kmModel5$cluster == x)) %>% climatology())

kmedias.pp <- bindGrid(lista, dimension = "member", skip.temporal.check = TRUE)

spatialPlot(kmedias.pp,backdrop.theme = 'countries', rev.color = T, as.table = T, names.attr = paste("Days in cluster", 1:k, ":",kmModel5$size[1:k]))
```
```{r}
cl1 <- subsetDimension(pp_reanalysis, dimension = "time", indices = which(kmModel5$cluster == 1))
cl2 <- subsetDimension(pp_reanalysis, dimension = "time", indices = which(kmModel5$cluster == 2))
cl3 <- subsetDimension(pp_reanalysis, dimension = "time", indices = which(kmModel5$cluster == 3))
cl4 <- subsetDimension(pp_reanalysis, dimension = "time", indices = which(kmModel5$cluster == 4))
cl5 <- subsetDimension(pp_reanalysis, dimension = "time", indices = which(kmModel5$cluster == 5))

cyclones.cl.1 <- cyclones[which(kmModel5$cluster ==1 ),]
cyclones.cl.2 <- cyclones[which(kmModel5$cluster ==2 ),]
cyclones.cl.3 <- cyclones[which(kmModel5$cluster ==3 ),]
cyclones.cl.4 <- cyclones[which(kmModel5$cluster ==4 ),]
cyclones.cl.5 <- cyclones[which(kmModel5$cluster ==5 ),]

cluster1 <- c()
cluster2 <- c()
cluster3 <- c()
cluster4 <- c()
cluster5 <- c()

cyc.cluster1 <- c()
cyc.cluster2 <- c()
cyc.cluster3 <- c()
cyc.cluster4 <- c()
cyc.cluster5 <- c()

for (i in c(1:12)) {
  cluster1 <- c(cluster1, length(subsetSeason(cl1, season = i)$Dates$start))
  cluster2 <- c(cluster2, length(subsetSeason(cl2, season = i)$Dates$start))
  cluster3 <- c(cluster3, length(subsetSeason(cl3, season = i)$Dates$start))
  cluster4 <- c(cluster4, length(subsetSeason(cl4, season = i)$Dates$start))
  cluster5 <- c(cluster5, length(subsetSeason(cl5, season = i)$Dates$start))
  
  idx <- which(as.numeric(format(cyclones.cl.1$Date, "%m")) == i)
  cyc.cluster1 <- c(cyc.cluster1,sum(cyclones.cl.1$cyclones_generation_centers[idx]))
  idx <- which(as.numeric(format(cyclones.cl.2$Date, "%m")) == i)
  cyc.cluster2 <- c(cyc.cluster2,sum(cyclones.cl.2$cyclones_generation_centers[idx]))
  idx <- which(as.numeric(format(cyclones.cl.3$Date, "%m")) == i)
  cyc.cluster3 <- c(cyc.cluster3,sum(cyclones.cl.3$cyclones_generation_centers[idx]))
  idx <- which(as.numeric(format(cyclones.cl.4$Date, "%m")) == i)
  cyc.cluster4 <- c(cyc.cluster4,sum(cyclones.cl.4$cyclones_generation_centers[idx]))
  idx <- which(as.numeric(format(cyclones.cl.5$Date, "%m")) == i)
  cyc.cluster5 <- c(cyc.cluster5,sum(cyclones.cl.5$cyclones_generation_centers[idx]))
}

x <- seq(1,5)
y <- seq(1,12)
data <- expand.grid(X=x, Y=y)
data$Z <- as.vector(t(matrix(c(cluster1,cluster2,cluster3,cluster4,cluster5), nrow = 12,ncol = 5)))

cyc.data <- expand.grid(X=x, Y=y)
cyc.data$Z <- as.vector(t(matrix(c(cyc.cluster1,cyc.cluster2,cyc.cluster3,cyc.cluster4,cyc.cluster5), nrow = 12,ncol = 5)))
levelplot(Z ~ X*Y, data=data  ,xlab="WT", ylab = "Month",
          main="", col.regions = rev(hcl.colors(100,palette = 'inferno')))
```
```{r}
coordinates(cyc.data) <- ~X+Y
```

In the next chunk, cyclones that appear each month are added to the levelplot.
```{r}
levelplot(Z ~ X*Y, data=data  ,xlab="WT", ylab = "Month",
          main="", col.regions = rev(hcl.colors(100,palette = 'inferno')))+    layer(sp.points(cyc.data, pch = 19, cex = cyc.data$Z/550, col = 'blue'))
```

```{r}
b <- boxplot(aggregateGrid(pp_reanalysis, aggr.lat = list(FUN = "mean"), aggr.lon = list(FUN = "mean"))$Data~kmModel5$cluster, main = "Precipitation Data for each cluster")
```
```{r}
violinPlot("Cluster1" = subsetGrid(kmedias.pp, members = 1), "Cluster2" = subsetGrid(kmedias.pp, members = 2),"Cluster3" = subsetGrid(kmedias.pp, members = 3),"Cluster4" = subsetGrid(kmedias.pp, members = 4), "Cluster5" = subsetGrid(kmedias.pp, members = 5))
```



MaxReturnValue function is computed to calculate the Maximum Return Value in 20 years index.
```{r}
MaxReturnValue <- function(data){
  #library(lubridate)
  #nyears <- round(time_length(difftime(cal.madrid.eqm$Dates$end[length(cal.madrid.eqm$Dates$end)], cal.madrid.eqm$Dates$start[1]),"years"))
  nyears <- 20
  data.maxYear <- aggregateGrid(redim(data), aggr.y = list(FUN = "max",na.rm = TRUE))

  data.maxrv <- climatology(data, clim.fun = list(FUN = "mean", na.rm = T))

  auxData <- data.maxYear$Data
  auxData[which(is.infinite(auxData))] <- NA

  if (any(!is.na(auxData))){
      auxGEV <- fgev(auxData)
      if ((auxGEV$estimate[3] - auxGEV$std.err[3] < 0) & (0  < auxGEV$estimate[3] + auxGEV$std.err[3])){
        auxGEV <- fgev(auxData, shape = 0)
        auxRV <- qgev(1-1/nyears, loc = auxGEV$estimate[1], scale = auxGEV$estimate[2], shape = 0)
      }else{
        auxRV <- qgev(1-1/nyears, loc = auxGEV$estimate[1], scale = auxGEV$estimate[2], shape = auxGEV$estimate[3])
      }
      data.maxrv <- as.numeric(auxRV)
      names(data.maxrv) <- paste("RV",nyears,"_max", sep = "")
  }
  return(data.maxrv)
  }
```

```{r}
severalQQplot <- function(obs, trmm , obs.cl1, obs.cl2,obs.cl3,obs.cl4,
                          obs.cl5,wt1, wt2, wt3, wt4, wt5,obs.cl6, wt6){
  qqplot(obs$Data[!is.na(obs$Data)], trmm$Data[!is.na(obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)

abline(a = 0, b = 1)

points(sort(obs.cl1$Data[!is.na(obs.cl1$Data)]), sort(wt1$Data[!is.na(obs.cl1$Data)]), col = "pink", pch = 4, cex = .5)
points(sort(obs.cl2$Data[!is.na(obs.cl2$Data)]), sort(wt2$Data[!is.na(obs.cl2$Data)]), col = "red", pch = 4, cex = .5)
points(sort(obs.cl3$Data[!is.na(obs.cl3$Data)]), sort(wt3$Data[!is.na(obs.cl3$Data)]), col = "blue", pch = 19, cex = .5)
points(sort(obs.cl4$Data[!is.na(obs.cl4$Data)]), sort(wt4$Data[!is.na(obs.cl4$Data)]), col = "gold", pch = 19, cex = .5)
points(sort(obs.cl5$Data[!is.na(obs.cl5$Data)]), sort(wt5$Data[!is.na(obs.cl5$Data)]), col = "forestgreen", pch = 19, cex = .5)

if(!is.null(wt6)){
  points(sort(obs.cl6$Data[!is.na(obs.cl6$Data)]), sort(wt6$Data[!is.na(obs.cl6$Data)]), col = "cyan", pch = 4, cex = .5)
  legend("topleft", legend = c("TRMM","WT1", "WT2","WT3","WT4","WT5","WT6"), pch = c(2,4,4,19,19,19,4), col = c("black", "pink","red","blue","gold","forestgreen","cyan"), cex = .75)
}else{
  legend("topleft", legend = c("TRMM","WT1", "WT2","WT3","WT4","WT5"), pch = c(2,4,4,19,19,19), col = c("black", "pink","red","blue","gold","forestgreen"), cex = .75)
}



grid() 
}

```

Finally, PACRAIN and TRMM precipitation data is loaded using loadeR funciton loadStationData. This data readout is easy and fast since both datasets are established in a ASCII format for each of the 7 PACRAIN station existing in our target area. Obviously, precip_obs is related with PACRAIN data and precip_trmm with TRMM data.

```{r}
precip_obs <- loadStationData("SP_ascii.zip", var = "precip_obs")

```

```{r}
precip_trmm <- loadStationData("SP_ascii.zip", var = "precip_trmm")

```
```{r}
pp_reanalysis <- subsetYears(pp_reanalysis, years = 1998:2019)
```

# Assessment in PACRAIN stations

## Kolopelu (Wallis and Futuna) Station

### Raw not conditioned data

Target station data(TRMM and PACRAIN) selection.
```{r}
i=1

station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])

idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
lon <- pp_reanalysis$xyCoords$x[idx]

idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
lat <- pp_reanalysis$xyCoords$y[idx2]

station.era5 <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)

```



```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
temporalPlot(station.obs,station.era5, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```

```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

index.reanalysis <- valueIndex1D(station.era5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.reanalysis.rv20max <- MaxReturnValue(station.era5)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r eval=TRUE, message=FALSE}
cal.station <- biasCorrection(y = station.obs, x = station.trmm, newdata = station.trmm, precipitation = TRUE, cross.val = "loo", method = "eqm")

cal.station$Dates$start <- as.POSIXct(cal.station$Dates$start,tz = "GMT")
cal.station$Dates$end <- as.POSIXct(cal.station$Dates$end,tz = "GMT")


index.cal.station <- valueIndex1D(cal.station$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))


index.cal.station.rv20max <- MaxReturnValue(cal.station)

index.cal.station <- c(index.cal.station, index.cal.station.rv20max)
```


```{r}
df <- data.frame(index.obs,index.trmm, index.reanalysis, index.cal.station)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```

```{r}
qqplot(station.obs$Data[!is.na(station.obs$Data)], cal.station$Data[!is.na(station.obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)

abline(a = 0, b = 1)

points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.era5$Data[!is.na(station.obs$Data)][-1]), col = "red", pch = 4, cex = .5)
points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.trmm$Data[!is.na(station.obs$Data)][-1]), col = "blue", pch = 4, cex = .5)

legend("topleft", legend = c("EQM","ERA5", "TRMM"), pch = c(2,4,4), col = c("black", "red","blue"))

grid() 
```


### Assessment conditioned on WT

#### k=5

```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.reanalysis.cl1 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 1))
station.reanalysis.cl2 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 2))
station.reanalysis.cl3 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 3))
station.reanalysis.cl4 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 4))
station.reanalysis.cl5 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.cal.cl1 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 1))
station.cal.cl2 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 2))
station.cal.cl3 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 3))
station.cal.cl4 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 4))
station.cal.cl5 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 5))
```


```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)

index.reanalysis.cl1 <- valueIndex1D(station.reanalysis.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl1 <- c(index.reanalysis.cl1, valueIndex1D(station.reanalysis.cl1$Data[!is.na(station.reanalysis.cl1$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl1.rv20max <- MaxReturnValue(station.reanalysis.cl1)

index.cal.cl1 <- valueIndex1D(station.cal.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl1 <- c(index.cal.cl1, valueIndex1D(station.cal.cl1$Data[!is.na(station.cal.cl1$Data)], index.codes = "P98WetAmount"))
index.cal.cl1.rv20max <- MaxReturnValue(station.cal.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
index.reanalysis.cl1 <- c(index.reanalysis.cl1, index.reanalysis.cl1.rv20max)
index.cal.cl1 <- c(index.cal.cl1, index.cal.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1, index.reanalysis.cl1, index.cal.cl1)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)

index.reanalysis.cl2 <- valueIndex1D(station.reanalysis.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl2 <- c(index.reanalysis.cl2, valueIndex1D(station.reanalysis.cl2$Data[!is.na(station.reanalysis.cl2$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl2.rv20max <- MaxReturnValue(station.reanalysis.cl2)

index.cal.cl2 <- valueIndex1D(station.cal.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl2 <- c(index.cal.cl2, valueIndex1D(station.cal.cl2$Data[!is.na(station.cal.cl2$Data)], index.codes = "P98WetAmount"))
index.cal.cl2.rv20max <- MaxReturnValue(station.cal.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
index.reanalysis.cl2 <- c(index.reanalysis.cl2, index.reanalysis.cl2.rv20max)
index.cal.cl2 <- c(index.cal.cl2, index.cal.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2, index.reanalysis.cl2, index.cal.cl2)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)

index.reanalysis.cl3 <- valueIndex1D(station.reanalysis.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl3 <- c(index.reanalysis.cl3, valueIndex1D(station.reanalysis.cl3$Data[!is.na(station.reanalysis.cl3$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl3.rv20max <- MaxReturnValue(station.reanalysis.cl3)

index.cal.cl3 <- valueIndex1D(station.cal.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl3 <- c(index.cal.cl3, valueIndex1D(station.cal.cl3$Data[!is.na(station.cal.cl3$Data)], index.codes = "P98WetAmount"))
index.cal.cl3.rv20max <- MaxReturnValue(station.cal.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
index.reanalysis.cl3 <- c(index.reanalysis.cl3, index.reanalysis.cl3.rv20max)
index.cal.cl3 <- c(index.cal.cl3, index.cal.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3, index.reanalysis.cl3, index.cal.cl3)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)

index.reanalysis.cl4 <- valueIndex1D(station.reanalysis.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl4 <- c(index.reanalysis.cl4, valueIndex1D(station.reanalysis.cl4$Data[!is.na(station.reanalysis.cl4$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl4.rv20max <- MaxReturnValue(station.reanalysis.cl4)

index.cal.cl4 <- valueIndex1D(station.cal.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl4 <- c(index.cal.cl4, valueIndex1D(station.cal.cl4$Data[!is.na(station.cal.cl4$Data)], index.codes = "P98WetAmount"))
index.cal.cl4.rv20max <- MaxReturnValue(station.cal.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
index.reanalysis.cl4 <- c(index.reanalysis.cl4, index.reanalysis.cl4.rv20max)
index.cal.cl4 <- c(index.cal.cl4, index.cal.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4, index.reanalysis.cl4, index.cal.cl4)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)

index.reanalysis.cl5 <- valueIndex1D(station.reanalysis.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl5 <- c(index.reanalysis.cl5, valueIndex1D(station.reanalysis.cl5$Data[!is.na(station.reanalysis.cl5$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl5.rv20max <- MaxReturnValue(station.reanalysis.cl5)

index.cal.cl5 <- valueIndex1D(station.cal.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl5 <- c(index.cal.cl5, valueIndex1D(station.cal.cl5$Data[!is.na(station.cal.cl5$Data)], index.codes = "P98WetAmount"))
index.cal.cl5.rv20max <- MaxReturnValue(station.cal.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
index.reanalysis.cl5 <- c(index.reanalysis.cl5, index.reanalysis.cl5.rv20max)
index.cal.cl5 <- c(index.cal.cl5, index.cal.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5, index.reanalysis.cl5, index.cal.cl5)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and TRMM raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

##### Difference between obs and ERA5-Reanalysis raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.reanalysis-index.obs),abs(index.reanalysis.cl1-index.obs.cl1),
                      abs(index.reanalysis.cl2-index.obs.cl2), abs(index.reanalysis.cl3-index.obs.cl3), abs(index.reanalysis.cl4-index.obs.cl4), abs(index.reanalysis.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```
```{r}
severalQQplot(station.obs, station.trmm, station.obs.cl1, station.obs.cl2, station.obs.cl3, station.obs.cl4,station.obs.cl5, station.cal.cl1, station.cal.cl2,
              station.cal.cl3, station.cal.cl4, station.cal.cl5, obs.cl6 = NULL, wt6 = NULL)
```



## Hakupu (Niue) station

### Raw not conditioned data
```{r}
i=2


station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])

idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
lon <- pp_reanalysis$xyCoords$x[idx]

idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
lat <- pp_reanalysis$xyCoords$y[idx2]

station.era5 <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)

```



```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
temporalPlot(station.obs,station.era5, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```

```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

index.reanalysis <- valueIndex1D(station.era5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.reanalysis.rv20max <- MaxReturnValue(station.era5)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r eval=TRUE, message=FALSE}
cal.station <- biasCorrection(y = station.obs, x = station.trmm, newdata = station.trmm, precipitation = TRUE, cross.val = "loo", method = "eqm")

cal.station$Dates$start <- as.POSIXct(cal.station$Dates$start,tz = "GMT")
cal.station$Dates$end <- as.POSIXct(cal.station$Dates$end,tz = "GMT")


index.cal.station <- valueIndex1D(cal.station$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))


index.cal.station.rv20max <- MaxReturnValue(cal.station)

index.cal.station <- c(index.cal.station, index.cal.station.rv20max)
```


```{r}
df <- data.frame(index.obs,index.trmm, index.reanalysis, index.cal.station)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```

```{r}
qqplot(station.obs$Data[!is.na(station.obs$Data)], cal.station$Data[!is.na(station.obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)

abline(a = 0, b = 1)

points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.era5$Data[!is.na(station.obs$Data)][-1]), col = "red", pch = 4, cex = .5)
points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.trmm$Data[!is.na(station.obs$Data)][-1]), col = "blue", pch = 4, cex = .5)

legend("topleft", legend = c("EQM","ERA5", "TRMM"), pch = c(2,4,4), col = c("black", "red","blue"))

grid() 
```


### Assessment conditioned on WT

#### k=5

```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.reanalysis.cl1 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 1))
station.reanalysis.cl2 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 2))
station.reanalysis.cl3 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 3))
station.reanalysis.cl4 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 4))
station.reanalysis.cl5 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.cal.cl1 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 1))
station.cal.cl2 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 2))
station.cal.cl3 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 3))
station.cal.cl4 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 4))
station.cal.cl5 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 5))
```


```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)

index.reanalysis.cl1 <- valueIndex1D(station.reanalysis.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl1 <- c(index.reanalysis.cl1, valueIndex1D(station.reanalysis.cl1$Data[!is.na(station.reanalysis.cl1$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl1.rv20max <- MaxReturnValue(station.reanalysis.cl1)

index.cal.cl1 <- valueIndex1D(station.cal.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl1 <- c(index.cal.cl1, valueIndex1D(station.cal.cl1$Data[!is.na(station.cal.cl1$Data)], index.codes = "P98WetAmount"))
index.cal.cl1.rv20max <- MaxReturnValue(station.cal.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
index.reanalysis.cl1 <- c(index.reanalysis.cl1, index.reanalysis.cl1.rv20max)
index.cal.cl1 <- c(index.cal.cl1, index.cal.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1, index.reanalysis.cl1, index.cal.cl1)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)

index.reanalysis.cl2 <- valueIndex1D(station.reanalysis.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl2 <- c(index.reanalysis.cl2, valueIndex1D(station.reanalysis.cl2$Data[!is.na(station.reanalysis.cl2$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl2.rv20max <- MaxReturnValue(station.reanalysis.cl2)

index.cal.cl2 <- valueIndex1D(station.cal.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl2 <- c(index.cal.cl2, valueIndex1D(station.cal.cl2$Data[!is.na(station.cal.cl2$Data)], index.codes = "P98WetAmount"))
index.cal.cl2.rv20max <- MaxReturnValue(station.cal.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
index.reanalysis.cl2 <- c(index.reanalysis.cl2, index.reanalysis.cl2.rv20max)
index.cal.cl2 <- c(index.cal.cl2, index.cal.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2, index.reanalysis.cl2, index.cal.cl2)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)

index.reanalysis.cl3 <- valueIndex1D(station.reanalysis.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl3 <- c(index.reanalysis.cl3, valueIndex1D(station.reanalysis.cl3$Data[!is.na(station.reanalysis.cl3$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl3.rv20max <- MaxReturnValue(station.reanalysis.cl3)

index.cal.cl3 <- valueIndex1D(station.cal.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl3 <- c(index.cal.cl3, valueIndex1D(station.cal.cl3$Data[!is.na(station.cal.cl3$Data)], index.codes = "P98WetAmount"))
index.cal.cl3.rv20max <- MaxReturnValue(station.cal.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
index.reanalysis.cl3 <- c(index.reanalysis.cl3, index.reanalysis.cl3.rv20max)
index.cal.cl3 <- c(index.cal.cl3, index.cal.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3, index.reanalysis.cl3, index.cal.cl3)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)

index.reanalysis.cl4 <- valueIndex1D(station.reanalysis.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl4 <- c(index.reanalysis.cl4, valueIndex1D(station.reanalysis.cl4$Data[!is.na(station.reanalysis.cl4$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl4.rv20max <- MaxReturnValue(station.reanalysis.cl4)

index.cal.cl4 <- valueIndex1D(station.cal.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl4 <- c(index.cal.cl4, valueIndex1D(station.cal.cl4$Data[!is.na(station.cal.cl4$Data)], index.codes = "P98WetAmount"))
index.cal.cl4.rv20max <- MaxReturnValue(station.cal.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
index.reanalysis.cl4 <- c(index.reanalysis.cl4, index.reanalysis.cl4.rv20max)
index.cal.cl4 <- c(index.cal.cl4, index.cal.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4, index.reanalysis.cl4, index.cal.cl4)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)

index.reanalysis.cl5 <- valueIndex1D(station.reanalysis.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl5 <- c(index.reanalysis.cl5, valueIndex1D(station.reanalysis.cl5$Data[!is.na(station.reanalysis.cl5$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl5.rv20max <- MaxReturnValue(station.reanalysis.cl5)

index.cal.cl5 <- valueIndex1D(station.cal.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl5 <- c(index.cal.cl5, valueIndex1D(station.cal.cl5$Data[!is.na(station.cal.cl5$Data)], index.codes = "P98WetAmount"))
index.cal.cl5.rv20max <- MaxReturnValue(station.cal.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
index.reanalysis.cl5 <- c(index.reanalysis.cl5, index.reanalysis.cl5.rv20max)
index.cal.cl5 <- c(index.cal.cl5, index.cal.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5, index.reanalysis.cl5, index.cal.cl5)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and TRMM raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

##### Difference between obs and ERA5-Reanalysis raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.reanalysis-index.obs),abs(index.reanalysis.cl1-index.obs.cl1),
                      abs(index.reanalysis.cl2-index.obs.cl2), abs(index.reanalysis.cl3-index.obs.cl3), abs(index.reanalysis.cl4-index.obs.cl4), abs(index.reanalysis.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```
```{r}
severalQQplot(station.obs, station.trmm, station.obs.cl1, station.obs.cl2, station.obs.cl3, station.obs.cl4,station.obs.cl5, station.cal.cl1, station.cal.cl2,
              station.cal.cl3, station.cal.cl4, station.cal.cl5, obs.cl6 = NULL, wt6 = NULL)
```



## Rarotonga International Airport (Cook Island) station

### Raw not conditioned data
```{r}
i=3


station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])

idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
lon <- pp_reanalysis$xyCoords$x[idx]

idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
lat <- pp_reanalysis$xyCoords$y[idx2]

station.era5 <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)

```



```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
temporalPlot(station.obs,station.era5, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```

```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

index.reanalysis <- valueIndex1D(station.era5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.reanalysis.rv20max <- MaxReturnValue(station.era5)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r eval=TRUE, message=FALSE}
cal.station <- biasCorrection(y = station.obs, x = station.trmm, newdata = station.trmm, precipitation = TRUE, cross.val = "loo", method = "eqm")

cal.station$Dates$start <- as.POSIXct(cal.station$Dates$start,tz = "GMT")
cal.station$Dates$end <- as.POSIXct(cal.station$Dates$end,tz = "GMT")


index.cal.station <- valueIndex1D(cal.station$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))


index.cal.station.rv20max <- MaxReturnValue(cal.station)

index.cal.station <- c(index.cal.station, index.cal.station.rv20max)
```


```{r}
df <- data.frame(index.obs,index.trmm, index.reanalysis, index.cal.station)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```

```{r}
qqplot(station.obs$Data[!is.na(station.obs$Data)], cal.station$Data[!is.na(station.obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)

abline(a = 0, b = 1)

points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.era5$Data[!is.na(station.obs$Data)]), col = "red", pch = 4, cex = .5)
points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.trmm$Data[!is.na(station.obs$Data)]), col = "blue", pch = 4, cex = .5)

legend("topleft", legend = c("EQM","ERA5", "TRMM"), pch = c(2,4,4), col = c("black", "red","blue"))

grid() 
```


### Assessment conditioned on WT

#### k=5

```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.reanalysis.cl1 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 1))
station.reanalysis.cl2 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 2))
station.reanalysis.cl3 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 3))
station.reanalysis.cl4 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 4))
station.reanalysis.cl5 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.cal.cl1 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 1))
station.cal.cl2 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 2))
station.cal.cl3 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 3))
station.cal.cl4 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 4))
station.cal.cl5 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 5))
```


```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)

index.reanalysis.cl1 <- valueIndex1D(station.reanalysis.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl1 <- c(index.reanalysis.cl1, valueIndex1D(station.reanalysis.cl1$Data[!is.na(station.reanalysis.cl1$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl1.rv20max <- MaxReturnValue(station.reanalysis.cl1)

index.cal.cl1 <- valueIndex1D(station.cal.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl1 <- c(index.cal.cl1, valueIndex1D(station.cal.cl1$Data[!is.na(station.cal.cl1$Data)], index.codes = "P98WetAmount"))
index.cal.cl1.rv20max <- MaxReturnValue(station.cal.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
index.reanalysis.cl1 <- c(index.reanalysis.cl1, index.reanalysis.cl1.rv20max)
index.cal.cl1 <- c(index.cal.cl1, index.cal.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1, index.reanalysis.cl1, index.cal.cl1)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)

index.reanalysis.cl2 <- valueIndex1D(station.reanalysis.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl2 <- c(index.reanalysis.cl2, valueIndex1D(station.reanalysis.cl2$Data[!is.na(station.reanalysis.cl2$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl2.rv20max <- MaxReturnValue(station.reanalysis.cl2)

index.cal.cl2 <- valueIndex1D(station.cal.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl2 <- c(index.cal.cl2, valueIndex1D(station.cal.cl2$Data[!is.na(station.cal.cl2$Data)], index.codes = "P98WetAmount"))
index.cal.cl2.rv20max <- MaxReturnValue(station.cal.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
index.reanalysis.cl2 <- c(index.reanalysis.cl2, index.reanalysis.cl2.rv20max)
index.cal.cl2 <- c(index.cal.cl2, index.cal.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2, index.reanalysis.cl2, index.cal.cl2)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)

index.reanalysis.cl3 <- valueIndex1D(station.reanalysis.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl3 <- c(index.reanalysis.cl3, valueIndex1D(station.reanalysis.cl3$Data[!is.na(station.reanalysis.cl3$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl3.rv20max <- MaxReturnValue(station.reanalysis.cl3)

index.cal.cl3 <- valueIndex1D(station.cal.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl3 <- c(index.cal.cl3, valueIndex1D(station.cal.cl3$Data[!is.na(station.cal.cl3$Data)], index.codes = "P98WetAmount"))
index.cal.cl3.rv20max <- MaxReturnValue(station.cal.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
index.reanalysis.cl3 <- c(index.reanalysis.cl3, index.reanalysis.cl3.rv20max)
index.cal.cl3 <- c(index.cal.cl3, index.cal.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3, index.reanalysis.cl3, index.cal.cl3)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)

index.reanalysis.cl4 <- valueIndex1D(station.reanalysis.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl4 <- c(index.reanalysis.cl4, valueIndex1D(station.reanalysis.cl4$Data[!is.na(station.reanalysis.cl4$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl4.rv20max <- MaxReturnValue(station.reanalysis.cl4)

index.cal.cl4 <- valueIndex1D(station.cal.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl4 <- c(index.cal.cl4, valueIndex1D(station.cal.cl4$Data[!is.na(station.cal.cl4$Data)], index.codes = "P98WetAmount"))
index.cal.cl4.rv20max <- MaxReturnValue(station.cal.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
index.reanalysis.cl4 <- c(index.reanalysis.cl4, index.reanalysis.cl4.rv20max)
index.cal.cl4 <- c(index.cal.cl4, index.cal.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4, index.reanalysis.cl4, index.cal.cl4)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)

index.reanalysis.cl5 <- valueIndex1D(station.reanalysis.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl5 <- c(index.reanalysis.cl5, valueIndex1D(station.reanalysis.cl5$Data[!is.na(station.reanalysis.cl5$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl5.rv20max <- MaxReturnValue(station.reanalysis.cl5)

index.cal.cl5 <- valueIndex1D(station.cal.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl5 <- c(index.cal.cl5, valueIndex1D(station.cal.cl5$Data[!is.na(station.cal.cl5$Data)], index.codes = "P98WetAmount"))
index.cal.cl5.rv20max <- MaxReturnValue(station.cal.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
index.reanalysis.cl5 <- c(index.reanalysis.cl5, index.reanalysis.cl5.rv20max)
index.cal.cl5 <- c(index.cal.cl5, index.cal.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5, index.reanalysis.cl5, index.cal.cl5)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and TRMM raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

##### Difference between obs and ERA5-Reanalysis raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.reanalysis-index.obs),abs(index.reanalysis.cl1-index.obs.cl1),
                      abs(index.reanalysis.cl2-index.obs.cl2), abs(index.reanalysis.cl3-index.obs.cl3), abs(index.reanalysis.cl4-index.obs.cl4), abs(index.reanalysis.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```
```{r}
severalQQplot(station.obs, station.trmm, station.obs.cl1, station.obs.cl2, station.obs.cl3, station.obs.cl4,station.obs.cl5, station.cal.cl1, station.cal.cl2,
              station.cal.cl3, station.cal.cl4, station.cal.cl5, obs.cl6 = NULL, wt6 = NULL)
```



## Bells Beach (New Zealand) station

### Raw not conditioned data
```{r}
i=4


station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])

idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
lon <- pp_reanalysis$xyCoords$x[idx]

idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
lat <- pp_reanalysis$xyCoords$y[idx2]

station.era5 <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)

```



```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
temporalPlot(station.obs,station.era5, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```

```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

index.reanalysis <- valueIndex1D(station.era5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.reanalysis.rv20max <- MaxReturnValue(station.era5)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r eval=TRUE, message=FALSE}
cal.station <- biasCorrection(y = station.obs, x = station.trmm, newdata = station.trmm, precipitation = TRUE, cross.val = "loo", method = "eqm")

cal.station$Dates$start <- as.POSIXct(cal.station$Dates$start,tz = "GMT")
cal.station$Dates$end <- as.POSIXct(cal.station$Dates$end,tz = "GMT")


index.cal.station <- valueIndex1D(cal.station$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))


index.cal.station.rv20max <- MaxReturnValue(cal.station)

index.cal.station <- c(index.cal.station, index.cal.station.rv20max)
```


```{r}
df <- data.frame(index.obs,index.trmm, index.reanalysis, index.cal.station)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```

```{r}
qqplot(station.obs$Data[!is.na(station.obs$Data)], cal.station$Data[!is.na(station.obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)

abline(a = 0, b = 1)

points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.era5$Data[!is.na(station.obs$Data)][-1]), col = "red", pch = 4, cex = .5)
points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.trmm$Data[!is.na(station.obs$Data)][-1]), col = "blue", pch = 4, cex = .5)

legend("topleft", legend = c("EQM","ERA5", "TRMM"), pch = c(2,4,4), col = c("black", "red","blue"))

grid() 
```


### Assessment conditioned on WT

#### k=5

```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.reanalysis.cl1 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 1))
station.reanalysis.cl2 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 2))
station.reanalysis.cl3 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 3))
station.reanalysis.cl4 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 4))
station.reanalysis.cl5 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.cal.cl1 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 1))
station.cal.cl2 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 2))
station.cal.cl3 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 3))
station.cal.cl4 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 4))
station.cal.cl5 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 5))
```


```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)

index.reanalysis.cl1 <- valueIndex1D(station.reanalysis.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl1 <- c(index.reanalysis.cl1, valueIndex1D(station.reanalysis.cl1$Data[!is.na(station.reanalysis.cl1$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl1.rv20max <- MaxReturnValue(station.reanalysis.cl1)

index.cal.cl1 <- valueIndex1D(station.cal.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl1 <- c(index.cal.cl1, valueIndex1D(station.cal.cl1$Data[!is.na(station.cal.cl1$Data)], index.codes = "P98WetAmount"))
index.cal.cl1.rv20max <- MaxReturnValue(station.cal.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
index.reanalysis.cl1 <- c(index.reanalysis.cl1, index.reanalysis.cl1.rv20max)
index.cal.cl1 <- c(index.cal.cl1, index.cal.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1, index.reanalysis.cl1, index.cal.cl1)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)

index.reanalysis.cl2 <- valueIndex1D(station.reanalysis.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl2 <- c(index.reanalysis.cl2, valueIndex1D(station.reanalysis.cl2$Data[!is.na(station.reanalysis.cl2$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl2.rv20max <- MaxReturnValue(station.reanalysis.cl2)

index.cal.cl2 <- valueIndex1D(station.cal.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl2 <- c(index.cal.cl2, valueIndex1D(station.cal.cl2$Data[!is.na(station.cal.cl2$Data)], index.codes = "P98WetAmount"))
index.cal.cl2.rv20max <- MaxReturnValue(station.cal.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
index.reanalysis.cl2 <- c(index.reanalysis.cl2, index.reanalysis.cl2.rv20max)
index.cal.cl2 <- c(index.cal.cl2, index.cal.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2, index.reanalysis.cl2, index.cal.cl2)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)

index.reanalysis.cl3 <- valueIndex1D(station.reanalysis.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl3 <- c(index.reanalysis.cl3, valueIndex1D(station.reanalysis.cl3$Data[!is.na(station.reanalysis.cl3$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl3.rv20max <- MaxReturnValue(station.reanalysis.cl3)

index.cal.cl3 <- valueIndex1D(station.cal.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl3 <- c(index.cal.cl3, valueIndex1D(station.cal.cl3$Data[!is.na(station.cal.cl3$Data)], index.codes = "P98WetAmount"))
index.cal.cl3.rv20max <- MaxReturnValue(station.cal.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
index.reanalysis.cl3 <- c(index.reanalysis.cl3, index.reanalysis.cl3.rv20max)
index.cal.cl3 <- c(index.cal.cl3, index.cal.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3, index.reanalysis.cl3, index.cal.cl3)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)

index.reanalysis.cl4 <- valueIndex1D(station.reanalysis.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl4 <- c(index.reanalysis.cl4, valueIndex1D(station.reanalysis.cl4$Data[!is.na(station.reanalysis.cl4$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl4.rv20max <- MaxReturnValue(station.reanalysis.cl4)

index.cal.cl4 <- valueIndex1D(station.cal.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl4 <- c(index.cal.cl4, valueIndex1D(station.cal.cl4$Data[!is.na(station.cal.cl4$Data)], index.codes = "P98WetAmount"))
index.cal.cl4.rv20max <- MaxReturnValue(station.cal.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
index.reanalysis.cl4 <- c(index.reanalysis.cl4, index.reanalysis.cl4.rv20max)
index.cal.cl4 <- c(index.cal.cl4, index.cal.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4, index.reanalysis.cl4, index.cal.cl4)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)

index.reanalysis.cl5 <- valueIndex1D(station.reanalysis.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl5 <- c(index.reanalysis.cl5, valueIndex1D(station.reanalysis.cl5$Data[!is.na(station.reanalysis.cl5$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl5.rv20max <- MaxReturnValue(station.reanalysis.cl5)

index.cal.cl5 <- valueIndex1D(station.cal.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl5 <- c(index.cal.cl5, valueIndex1D(station.cal.cl5$Data[!is.na(station.cal.cl5$Data)], index.codes = "P98WetAmount"))
index.cal.cl5.rv20max <- MaxReturnValue(station.cal.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
index.reanalysis.cl5 <- c(index.reanalysis.cl5, index.reanalysis.cl5.rv20max)
index.cal.cl5 <- c(index.cal.cl5, index.cal.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5, index.reanalysis.cl5, index.cal.cl5)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and TRMM raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

##### Difference between obs and ERA5-Reanalysis raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.reanalysis-index.obs),abs(index.reanalysis.cl1-index.obs.cl1),
                      abs(index.reanalysis.cl2-index.obs.cl2), abs(index.reanalysis.cl3-index.obs.cl3), abs(index.reanalysis.cl4-index.obs.cl4), abs(index.reanalysis.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```
```{r}
severalQQplot(station.obs, station.trmm, station.obs.cl1, station.obs.cl2, station.obs.cl3, station.obs.cl4,station.obs.cl5, station.cal.cl1, station.cal.cl2,
              station.cal.cl3, station.cal.cl4, station.cal.cl5, obs.cl6 = NULL, wt6 = NULL)
```



## Possible ocean buoy

### Raw not conditioned data
```{r}
i=5


station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])

idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
lon <- pp_reanalysis$xyCoords$x[idx]

idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
lat <- pp_reanalysis$xyCoords$y[idx2]

station.era5 <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)

```



```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
temporalPlot(station.obs,station.era5, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```

```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

index.reanalysis <- valueIndex1D(station.era5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.reanalysis.rv20max <- MaxReturnValue(station.era5)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r eval=TRUE, message=FALSE}
cal.station <- biasCorrection(y = station.obs, x = station.trmm, newdata = station.trmm, precipitation = TRUE, cross.val = "loo", method = "eqm")

cal.station$Dates$start <- as.POSIXct(cal.station$Dates$start,tz = "GMT")
cal.station$Dates$end <- as.POSIXct(cal.station$Dates$end,tz = "GMT")


index.cal.station <- valueIndex1D(cal.station$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))


index.cal.station.rv20max <- MaxReturnValue(cal.station)

index.cal.station <- c(index.cal.station, index.cal.station.rv20max)
```


```{r}
df <- data.frame(index.obs,index.trmm, index.reanalysis, index.cal.station)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```

```{r}
qqplot(station.obs$Data[!is.na(station.obs$Data)], cal.station$Data[!is.na(station.obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)

abline(a = 0, b = 1)

points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.era5$Data[!is.na(station.obs$Data)]), col = "red", pch = 4, cex = .5)
points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.trmm$Data[!is.na(station.obs$Data)]), col = "blue", pch = 4, cex = .5)

legend("topleft", legend = c("EQM","ERA5", "TRMM"), pch = c(2,4,4), col = c("black", "red","blue"))

grid() 
```


### Assessment conditioned on WT

#### k=5

```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.reanalysis.cl1 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 1))
station.reanalysis.cl2 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 2))
station.reanalysis.cl3 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 3))
station.reanalysis.cl4 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 4))
station.reanalysis.cl5 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.cal.cl1 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 1))
station.cal.cl2 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 2))
station.cal.cl3 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 3))
station.cal.cl4 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 4))
station.cal.cl5 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 5))
```


```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)

index.reanalysis.cl1 <- valueIndex1D(station.reanalysis.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl1 <- c(index.reanalysis.cl1, valueIndex1D(station.reanalysis.cl1$Data[!is.na(station.reanalysis.cl1$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl1.rv20max <- MaxReturnValue(station.reanalysis.cl1)

index.cal.cl1 <- valueIndex1D(station.cal.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl1 <- c(index.cal.cl1, valueIndex1D(station.cal.cl1$Data[!is.na(station.cal.cl1$Data)], index.codes = "P98WetAmount"))
index.cal.cl1.rv20max <- MaxReturnValue(station.cal.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
index.reanalysis.cl1 <- c(index.reanalysis.cl1, index.reanalysis.cl1.rv20max)
index.cal.cl1 <- c(index.cal.cl1, index.cal.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1, index.reanalysis.cl1, index.cal.cl1)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)

index.reanalysis.cl2 <- valueIndex1D(station.reanalysis.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl2 <- c(index.reanalysis.cl2, valueIndex1D(station.reanalysis.cl2$Data[!is.na(station.reanalysis.cl2$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl2.rv20max <- MaxReturnValue(station.reanalysis.cl2)

index.cal.cl2 <- valueIndex1D(station.cal.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl2 <- c(index.cal.cl2, valueIndex1D(station.cal.cl2$Data[!is.na(station.cal.cl2$Data)], index.codes = "P98WetAmount"))
index.cal.cl2.rv20max <- MaxReturnValue(station.cal.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
index.reanalysis.cl2 <- c(index.reanalysis.cl2, index.reanalysis.cl2.rv20max)
index.cal.cl2 <- c(index.cal.cl2, index.cal.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2, index.reanalysis.cl2, index.cal.cl2)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)

index.reanalysis.cl3 <- valueIndex1D(station.reanalysis.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl3 <- c(index.reanalysis.cl3, valueIndex1D(station.reanalysis.cl3$Data[!is.na(station.reanalysis.cl3$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl3.rv20max <- MaxReturnValue(station.reanalysis.cl3)

index.cal.cl3 <- valueIndex1D(station.cal.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl3 <- c(index.cal.cl3, valueIndex1D(station.cal.cl3$Data[!is.na(station.cal.cl3$Data)], index.codes = "P98WetAmount"))
index.cal.cl3.rv20max <- MaxReturnValue(station.cal.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
index.reanalysis.cl3 <- c(index.reanalysis.cl3, index.reanalysis.cl3.rv20max)
index.cal.cl3 <- c(index.cal.cl3, index.cal.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3, index.reanalysis.cl3, index.cal.cl3)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)

index.reanalysis.cl4 <- valueIndex1D(station.reanalysis.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl4 <- c(index.reanalysis.cl4, valueIndex1D(station.reanalysis.cl4$Data[!is.na(station.reanalysis.cl4$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl4.rv20max <- MaxReturnValue(station.reanalysis.cl4)

index.cal.cl4 <- valueIndex1D(station.cal.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl4 <- c(index.cal.cl4, valueIndex1D(station.cal.cl4$Data[!is.na(station.cal.cl4$Data)], index.codes = "P98WetAmount"))
index.cal.cl4.rv20max <- MaxReturnValue(station.cal.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
index.reanalysis.cl4 <- c(index.reanalysis.cl4, index.reanalysis.cl4.rv20max)
index.cal.cl4 <- c(index.cal.cl4, index.cal.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4, index.reanalysis.cl4, index.cal.cl4)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)

index.reanalysis.cl5 <- valueIndex1D(station.reanalysis.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl5 <- c(index.reanalysis.cl5, valueIndex1D(station.reanalysis.cl5$Data[!is.na(station.reanalysis.cl5$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl5.rv20max <- MaxReturnValue(station.reanalysis.cl5)

index.cal.cl5 <- valueIndex1D(station.cal.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl5 <- c(index.cal.cl5, valueIndex1D(station.cal.cl5$Data[!is.na(station.cal.cl5$Data)], index.codes = "P98WetAmount"))
index.cal.cl5.rv20max <- MaxReturnValue(station.cal.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
index.reanalysis.cl5 <- c(index.reanalysis.cl5, index.reanalysis.cl5.rv20max)
index.cal.cl5 <- c(index.cal.cl5, index.cal.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5, index.reanalysis.cl5, index.cal.cl5)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and TRMM raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

##### Difference between obs and ERA5-Reanalysis raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.reanalysis-index.obs),abs(index.reanalysis.cl1-index.obs.cl1),
                      abs(index.reanalysis.cl2-index.obs.cl2), abs(index.reanalysis.cl3-index.obs.cl3), abs(index.reanalysis.cl4-index.obs.cl4), abs(index.reanalysis.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```
```{r}
severalQQplot(station.obs, station.trmm, station.obs.cl1, station.obs.cl2, station.obs.cl3, station.obs.cl4,station.obs.cl5, station.cal.cl1, station.cal.cl2,
              station.cal.cl3, station.cal.cl4, station.cal.cl5, obs.cl6 = NULL, wt6 = NULL)
```



## Aoloau (American Samoa) station

### Raw not conditioned data
```{r}
i=6


station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])

idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
lon <- pp_reanalysis$xyCoords$x[idx]

idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
lat <- pp_reanalysis$xyCoords$y[idx2]

station.era5 <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)

```



```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
temporalPlot(station.obs,station.era5, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```

```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

index.reanalysis <- valueIndex1D(station.era5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.reanalysis.rv20max <- MaxReturnValue(station.era5)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r eval=TRUE, message=FALSE}
cal.station <- biasCorrection(y = station.obs, x = station.trmm, newdata = station.trmm, precipitation = TRUE, cross.val = "loo", method = "eqm")

cal.station$Dates$start <- as.POSIXct(cal.station$Dates$start,tz = "GMT")
cal.station$Dates$end <- as.POSIXct(cal.station$Dates$end,tz = "GMT")


index.cal.station <- valueIndex1D(cal.station$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))


index.cal.station.rv20max <- MaxReturnValue(cal.station)

index.cal.station <- c(index.cal.station, index.cal.station.rv20max)
```


```{r}
df <- data.frame(index.obs,index.trmm, index.reanalysis, index.cal.station)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```

```{r}
qqplot(station.obs$Data[!is.na(station.obs$Data)], cal.station$Data[!is.na(station.obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)

abline(a = 0, b = 1)

points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.era5$Data[!is.na(station.obs$Data)][-1]), col = "red", pch = 4, cex = .5)
points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.trmm$Data[!is.na(station.obs$Data)][-1]), col = "blue", pch = 4, cex = .5)

legend("topleft", legend = c("EQM","ERA5", "TRMM"), pch = c(2,4,4), col = c("black", "red","blue"))

grid() 
```


### Assessment conditioned on WT

#### k=5

```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.reanalysis.cl1 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 1))
station.reanalysis.cl2 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 2))
station.reanalysis.cl3 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 3))
station.reanalysis.cl4 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 4))
station.reanalysis.cl5 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.cal.cl1 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 1))
station.cal.cl2 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 2))
station.cal.cl3 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 3))
station.cal.cl4 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 4))
station.cal.cl5 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 5))
```


```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)

index.reanalysis.cl1 <- valueIndex1D(station.reanalysis.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl1 <- c(index.reanalysis.cl1, valueIndex1D(station.reanalysis.cl1$Data[!is.na(station.reanalysis.cl1$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl1.rv20max <- MaxReturnValue(station.reanalysis.cl1)

index.cal.cl1 <- valueIndex1D(station.cal.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl1 <- c(index.cal.cl1, valueIndex1D(station.cal.cl1$Data[!is.na(station.cal.cl1$Data)], index.codes = "P98WetAmount"))
index.cal.cl1.rv20max <- MaxReturnValue(station.cal.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
index.reanalysis.cl1 <- c(index.reanalysis.cl1, index.reanalysis.cl1.rv20max)
index.cal.cl1 <- c(index.cal.cl1, index.cal.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1, index.reanalysis.cl1, index.cal.cl1)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)

index.reanalysis.cl2 <- valueIndex1D(station.reanalysis.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl2 <- c(index.reanalysis.cl2, valueIndex1D(station.reanalysis.cl2$Data[!is.na(station.reanalysis.cl2$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl2.rv20max <- MaxReturnValue(station.reanalysis.cl2)

index.cal.cl2 <- valueIndex1D(station.cal.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl2 <- c(index.cal.cl2, valueIndex1D(station.cal.cl2$Data[!is.na(station.cal.cl2$Data)], index.codes = "P98WetAmount"))
index.cal.cl2.rv20max <- MaxReturnValue(station.cal.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
index.reanalysis.cl2 <- c(index.reanalysis.cl2, index.reanalysis.cl2.rv20max)
index.cal.cl2 <- c(index.cal.cl2, index.cal.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2, index.reanalysis.cl2, index.cal.cl2)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)

index.reanalysis.cl3 <- valueIndex1D(station.reanalysis.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl3 <- c(index.reanalysis.cl3, valueIndex1D(station.reanalysis.cl3$Data[!is.na(station.reanalysis.cl3$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl3.rv20max <- MaxReturnValue(station.reanalysis.cl3)

index.cal.cl3 <- valueIndex1D(station.cal.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl3 <- c(index.cal.cl3, valueIndex1D(station.cal.cl3$Data[!is.na(station.cal.cl3$Data)], index.codes = "P98WetAmount"))
index.cal.cl3.rv20max <- MaxReturnValue(station.cal.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
index.reanalysis.cl3 <- c(index.reanalysis.cl3, index.reanalysis.cl3.rv20max)
index.cal.cl3 <- c(index.cal.cl3, index.cal.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3, index.reanalysis.cl3, index.cal.cl3)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)

index.reanalysis.cl4 <- valueIndex1D(station.reanalysis.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl4 <- c(index.reanalysis.cl4, valueIndex1D(station.reanalysis.cl4$Data[!is.na(station.reanalysis.cl4$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl4.rv20max <- MaxReturnValue(station.reanalysis.cl4)

index.cal.cl4 <- valueIndex1D(station.cal.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl4 <- c(index.cal.cl4, valueIndex1D(station.cal.cl4$Data[!is.na(station.cal.cl4$Data)], index.codes = "P98WetAmount"))
index.cal.cl4.rv20max <- MaxReturnValue(station.cal.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
index.reanalysis.cl4 <- c(index.reanalysis.cl4, index.reanalysis.cl4.rv20max)
index.cal.cl4 <- c(index.cal.cl4, index.cal.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4, index.reanalysis.cl4, index.cal.cl4)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)

index.reanalysis.cl5 <- valueIndex1D(station.reanalysis.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl5 <- c(index.reanalysis.cl5, valueIndex1D(station.reanalysis.cl5$Data[!is.na(station.reanalysis.cl5$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl5.rv20max <- MaxReturnValue(station.reanalysis.cl5)

index.cal.cl5 <- valueIndex1D(station.cal.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl5 <- c(index.cal.cl5, valueIndex1D(station.cal.cl5$Data[!is.na(station.cal.cl5$Data)], index.codes = "P98WetAmount"))
index.cal.cl5.rv20max <- MaxReturnValue(station.cal.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
index.reanalysis.cl5 <- c(index.reanalysis.cl5, index.reanalysis.cl5.rv20max)
index.cal.cl5 <- c(index.cal.cl5, index.cal.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5, index.reanalysis.cl5, index.cal.cl5)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and TRMM raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

##### Difference between obs and ERA5-Reanalysis raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.reanalysis-index.obs),abs(index.reanalysis.cl1-index.obs.cl1),
                      abs(index.reanalysis.cl2-index.obs.cl2), abs(index.reanalysis.cl3-index.obs.cl3), abs(index.reanalysis.cl4-index.obs.cl4), abs(index.reanalysis.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```
```{r}
severalQQplot(station.obs, station.trmm, station.obs.cl1, station.obs.cl2, station.obs.cl3, station.obs.cl4,station.obs.cl5, station.cal.cl1, station.cal.cl2,
              station.cal.cl3, station.cal.cl4, station.cal.cl5, obs.cl6 = NULL, wt6 = NULL)
```
```{r}
station.cal.conditioned <- bindGrid(station.cal.cl1, station.cal.cl2, station.cal.cl3,
                                    station.cal.cl4, station.cal.cl5, dimension = "time")

qqplot(station.obs$Data[!is.na(station.obs$Data)], station.trmm$Data[!is.na(station.obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)
abline(a = 0, b = 1)
points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.cal.conditioned$Data[!is.na(station.obs$Data)]), col = "gold", pch = 19, cex = .5)
```



## Aoloau (American Samoa) station (low elevation)

### Raw not conditioned data
```{r}
i=7


station.trmm <- subsetGrid(precip_trmm, station.id = precip_trmm$Metadata$station_id[i])
station.obs <- subsetGrid(precip_obs, station.id = precip_trmm$Metadata$station_id[i])

idx <- which.min(abs(pp_reanalysis$xyCoords$x - station.obs$xyCoords$x))
lon <- pp_reanalysis$xyCoords$x[idx]

idx2 <- which.min(abs(pp_reanalysis$xyCoords$y - station.obs$xyCoords$y))
lat <- pp_reanalysis$xyCoords$y[idx2]

station.era5 <- subsetGrid(pp_reanalysis, lonLim = lon, latLim = lat)

```



```{r}
temporalPlot(station.obs,station.trmm, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```
```{r}
temporalPlot(station.obs,station.era5, xyplot.custom = list(main = paste("Precipitation in",station.trmm$Metadata$name,"(elevation",precip_trmm$Metadata$altitude[i],"m)"), ylab = "mm"))
```

```{r}
index.obs <- valueIndex1D(station.obs$Data[!is.na(station.obs$Data)],index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs <- c(index.obs, valueIndex1D(station.obs$Data[!is.na(station.obs$Data)], index.codes = "P98WetAmount"))
index.obs.rv20max <- MaxReturnValue(station.obs)

index.trmm <- valueIndex1D(station.trmm$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.trmm.rv20max <- MaxReturnValue(station.trmm)

index.reanalysis <- valueIndex1D(station.era5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))
index.reanalysis.rv20max <- MaxReturnValue(station.era5)
```
```{r}
index.obs <- c(index.obs, index.obs.rv20max)
index.trmm <- c(index.trmm, index.trmm.rv20max)
index.reanalysis <- c(index.reanalysis, index.reanalysis.rv20max)
```

```{r eval=TRUE, message=FALSE}
cal.station <- biasCorrection(y = station.obs, x = station.trmm, newdata = station.trmm, precipitation = TRUE, cross.val = "loo", method = "eqm")

cal.station$Dates$start <- as.POSIXct(cal.station$Dates$start,tz = "GMT")
cal.station$Dates$end <- as.POSIXct(cal.station$Dates$end,tz = "GMT")


index.cal.station <- valueIndex1D(cal.station$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet","P98WetAmount"))


index.cal.station.rv20max <- MaxReturnValue(cal.station)

index.cal.station <- c(index.cal.station, index.cal.station.rv20max)
```


```{r}
df <- data.frame(index.obs,index.trmm, index.reanalysis, index.cal.station)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```

```{r}
qqplot(station.obs$Data[!is.na(station.obs$Data)], cal.station$Data[!is.na(station.obs$Data)], main = paste(station.obs$Metadata$name), xlab = "Observed (mm)", ylab = "Predicted (mm)", col = "black", pch = 2, cex = .5)

abline(a = 0, b = 1)

points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.era5$Data[!is.na(station.obs$Data)][-1]), col = "red", pch = 4, cex = .5)
points(sort(station.obs$Data[!is.na(station.obs$Data)]), sort(station.trmm$Data[!is.na(station.obs$Data)][-1]), col = "blue", pch = 4, cex = .5)

legend("topleft", legend = c("EQM","ERA5", "TRMM"), pch = c(2,4,4), col = c("black", "red","blue"))

grid() 
```


### Assessment conditioned on WT

#### k=5

```{r}
station.obs.cl1 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 1))
station.obs.cl2 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 2))
station.obs.cl3 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 3))
station.obs.cl4 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 4))
station.obs.cl5 <- subsetDimension(station.obs, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.reanalysis.cl1 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 1))
station.reanalysis.cl2 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 2))
station.reanalysis.cl3 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 3))
station.reanalysis.cl4 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 4))
station.reanalysis.cl5 <- subsetDimension(station.era5, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.trmm.cl1 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 1))
station.trmm.cl2 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 2))
station.trmm.cl3 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 3))
station.trmm.cl4 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 4))
station.trmm.cl5 <- subsetDimension(station.trmm, dimension = "time", indices = which(kmModel5$cluster == 5))
```

```{r}
station.cal.cl1 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 1))
station.cal.cl2 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 2))
station.cal.cl3 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 3))
station.cal.cl4 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 4))
station.cal.cl5 <- subsetDimension(cal.station, dimension = "time", indices = which(kmModel5$cluster == 5))
```


```{r}
index.obs.cl1 <- valueIndex1D(station.obs.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl1 <- c(index.obs.cl1, valueIndex1D(station.obs.cl1$Data[!is.na(station.obs.cl1$Data)], index.codes = "P98WetAmount"))
index.obs.cl1.rv20max <- MaxReturnValue(station.obs.cl1)

index.trmm.cl1 <- valueIndex1D(station.trmm.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl1 <- c(index.trmm.cl1, valueIndex1D(station.trmm.cl1$Data[!is.na(station.trmm.cl1$Data)], index.codes = "P98WetAmount"))
index.trmm.cl1.rv20max <- MaxReturnValue(station.trmm.cl1)

index.reanalysis.cl1 <- valueIndex1D(station.reanalysis.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl1 <- c(index.reanalysis.cl1, valueIndex1D(station.reanalysis.cl1$Data[!is.na(station.reanalysis.cl1$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl1.rv20max <- MaxReturnValue(station.reanalysis.cl1)

index.cal.cl1 <- valueIndex1D(station.cal.cl1$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl1 <- c(index.cal.cl1, valueIndex1D(station.cal.cl1$Data[!is.na(station.cal.cl1$Data)], index.codes = "P98WetAmount"))
index.cal.cl1.rv20max <- MaxReturnValue(station.cal.cl1)
```

```{r}
index.obs.cl1 <- c(index.obs.cl1, index.obs.cl1.rv20max)
index.trmm.cl1 <- c(index.trmm.cl1, index.trmm.cl1.rv20max)
index.reanalysis.cl1 <- c(index.reanalysis.cl1, index.reanalysis.cl1.rv20max)
index.cal.cl1 <- c(index.cal.cl1, index.cal.cl1.rv20max)
```

##### Index assessment conditioned on WT1
```{r}
df <- data.frame(index.obs.cl1,index.trmm.cl1, index.reanalysis.cl1, index.cal.cl1)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Calibrated")
format(df, digits = 3, scientific = 5)
```
```{r}
index.obs.cl2 <- valueIndex1D(station.obs.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl2 <- c(index.obs.cl2, valueIndex1D(station.obs.cl2$Data[!is.na(station.obs.cl2$Data)], index.codes = "P98WetAmount"))
index.obs.cl2.rv20max <- MaxReturnValue(station.obs.cl2)

index.trmm.cl2 <- valueIndex1D(station.trmm.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl2 <- c(index.trmm.cl2, valueIndex1D(station.trmm.cl2$Data[!is.na(station.trmm.cl2$Data)], index.codes = "P98WetAmount"))
index.trmm.cl2.rv20max <- MaxReturnValue(station.trmm.cl2)

index.reanalysis.cl2 <- valueIndex1D(station.reanalysis.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl2 <- c(index.reanalysis.cl2, valueIndex1D(station.reanalysis.cl2$Data[!is.na(station.reanalysis.cl2$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl2.rv20max <- MaxReturnValue(station.reanalysis.cl2)

index.cal.cl2 <- valueIndex1D(station.cal.cl2$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl2 <- c(index.cal.cl2, valueIndex1D(station.cal.cl2$Data[!is.na(station.cal.cl2$Data)], index.codes = "P98WetAmount"))
index.cal.cl2.rv20max <- MaxReturnValue(station.cal.cl2)
```

```{r}
index.obs.cl2 <- c(index.obs.cl2, index.obs.cl2.rv20max)
index.trmm.cl2<- c(index.trmm.cl2, index.trmm.cl2.rv20max)
index.reanalysis.cl2 <- c(index.reanalysis.cl2, index.reanalysis.cl2.rv20max)
index.cal.cl2 <- c(index.cal.cl2, index.cal.cl2.rv20max)
```

##### Index assessment conditioned on WT2
```{r}
df <- data.frame(index.obs.cl2,index.trmm.cl2, index.reanalysis.cl2, index.cal.cl2)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```


```{r}
index.obs.cl3 <- valueIndex1D(station.obs.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl3 <- c(index.obs.cl3, valueIndex1D(station.obs.cl3$Data[!is.na(station.obs.cl3$Data)], index.codes = "P98WetAmount"))
index.obs.cl3.rv20max <- MaxReturnValue(station.obs.cl3)

index.trmm.cl3 <- valueIndex1D(station.trmm.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl3 <- c(index.trmm.cl3, valueIndex1D(station.trmm.cl3$Data[!is.na(station.trmm.cl3$Data)], index.codes = "P98WetAmount"))
index.trmm.cl3.rv20max <- MaxReturnValue(station.trmm.cl3)

index.reanalysis.cl3 <- valueIndex1D(station.reanalysis.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl3 <- c(index.reanalysis.cl3, valueIndex1D(station.reanalysis.cl3$Data[!is.na(station.reanalysis.cl3$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl3.rv20max <- MaxReturnValue(station.reanalysis.cl3)

index.cal.cl3 <- valueIndex1D(station.cal.cl3$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl3 <- c(index.cal.cl3, valueIndex1D(station.cal.cl3$Data[!is.na(station.cal.cl3$Data)], index.codes = "P98WetAmount"))
index.cal.cl3.rv20max <- MaxReturnValue(station.cal.cl3)
```

```{r}
index.obs.cl3 <- c(index.obs.cl3, index.obs.cl3.rv20max)
index.trmm.cl3 <- c(index.trmm.cl3, index.trmm.cl3.rv20max)
index.reanalysis.cl3 <- c(index.reanalysis.cl3, index.reanalysis.cl3.rv20max)
index.cal.cl3 <- c(index.cal.cl3, index.cal.cl3.rv20max)
```

##### Index assessment conditioned on WT3
```{r}
df <- data.frame(index.obs.cl3,index.trmm.cl3, index.reanalysis.cl3, index.cal.cl3)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl4 <- valueIndex1D(station.obs.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl4 <- c(index.obs.cl4, valueIndex1D(station.obs.cl4$Data[!is.na(station.obs.cl4$Data)], index.codes = "P98WetAmount"))
index.obs.cl4.rv20max <- MaxReturnValue(station.obs.cl4)

index.trmm.cl4 <- valueIndex1D(station.trmm.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl4 <- c(index.trmm.cl4, valueIndex1D(station.trmm.cl4$Data[!is.na(station.trmm.cl4$Data)], index.codes = "P98WetAmount"))
index.trmm.cl4.rv20max <- MaxReturnValue(station.trmm.cl4)

index.reanalysis.cl4 <- valueIndex1D(station.reanalysis.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl4 <- c(index.reanalysis.cl4, valueIndex1D(station.reanalysis.cl4$Data[!is.na(station.reanalysis.cl4$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl4.rv20max <- MaxReturnValue(station.reanalysis.cl4)

index.cal.cl4 <- valueIndex1D(station.cal.cl4$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl4 <- c(index.cal.cl4, valueIndex1D(station.cal.cl4$Data[!is.na(station.cal.cl4$Data)], index.codes = "P98WetAmount"))
index.cal.cl4.rv20max <- MaxReturnValue(station.cal.cl4)
```

```{r}
index.obs.cl4 <- c(index.obs.cl4, index.obs.cl4.rv20max)
index.trmm.cl4 <- c(index.trmm.cl4, index.trmm.cl4.rv20max)
index.reanalysis.cl4 <- c(index.reanalysis.cl4, index.reanalysis.cl4.rv20max)
index.cal.cl4 <- c(index.cal.cl4, index.cal.cl4.rv20max)
```

##### Index assessment conditioned on WT4
```{r}
df <- data.frame(index.obs.cl4,index.trmm.cl4, index.reanalysis.cl4, index.cal.cl4)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```

```{r}
index.obs.cl5 <- valueIndex1D(station.obs.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.obs.cl5 <- c(index.obs.cl5, valueIndex1D(station.obs.cl5$Data[!is.na(station.obs.cl5$Data)], index.codes = "P98WetAmount"))
index.obs.cl5.rv20max <- MaxReturnValue(station.obs.cl5)

index.trmm.cl5 <- valueIndex1D(station.trmm.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.trmm.cl5 <- c(index.trmm.cl5, valueIndex1D(station.trmm.cl5$Data[!is.na(station.trmm.cl5$Data)], index.codes = "P98WetAmount"))
index.trmm.cl5.rv20max <- MaxReturnValue(station.trmm.cl5)

index.reanalysis.cl5 <- valueIndex1D(station.reanalysis.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.reanalysis.cl5 <- c(index.reanalysis.cl5, valueIndex1D(station.reanalysis.cl5$Data[!is.na(station.reanalysis.cl5$Data)], index.codes = "P98WetAmount"))
index.reanalysis.cl5.rv20max <- MaxReturnValue(station.reanalysis.cl5)

index.cal.cl5 <- valueIndex1D(station.cal.cl5$Data,index.codes=c("Skewness","SDII","R10","R10p","R20","R20p","P98Wet"))
index.cal.cl5 <- c(index.cal.cl5, valueIndex1D(station.cal.cl5$Data[!is.na(station.cal.cl5$Data)], index.codes = "P98WetAmount"))
index.cal.cl5.rv20max <- MaxReturnValue(station.cal.cl5)
```

```{r}
index.obs.cl5 <- c(index.obs.cl5, index.obs.cl5.rv20max)
index.trmm.cl5 <- c(index.trmm.cl5, index.trmm.cl5.rv20max)
index.reanalysis.cl5 <- c(index.reanalysis.cl5, index.reanalysis.cl5.rv20max)
index.cal.cl5 <- c(index.cal.cl5, index.cal.cl5.rv20max)
```

##### Index assessment conditioned on WT5
```{r}
df <- data.frame(index.obs.cl5,index.trmm.cl5, index.reanalysis.cl5, index.cal.cl5)
colnames(df) <- c("Obs", "TRMM", "ERA5", "TRMM-Corrected")
format(df, digits = 3, scientific = 5)
```
##### Difference between obs and TRMM raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.trmm-index.obs),abs(index.trmm.cl1-index.obs.cl1),
                      abs(index.trmm.cl2-index.obs.cl2), abs(index.trmm.cl3-index.obs.cl3), abs(index.trmm.cl4-index.obs.cl4), abs(index.trmm.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```

##### Difference between obs and ERA5-Reanalysis raw/WT-conditioned data
```{r}
diff.df <- data.frame(abs(index.reanalysis-index.obs),abs(index.reanalysis.cl1-index.obs.cl1),
                      abs(index.reanalysis.cl2-index.obs.cl2), abs(index.reanalysis.cl3-index.obs.cl3), abs(index.reanalysis.cl4-index.obs.cl4), abs(index.reanalysis.cl5-index.obs.cl5)
                      )
colnames(diff.df) <- c("Raw","WT1", "WT2","WT3", "WT4","WT5")

format(diff.df, digits = 3, scientific = 5)
```
```{r}
severalQQplot(station.obs, station.trmm, station.obs.cl1, station.obs.cl2, station.obs.cl3, station.obs.cl4,station.obs.cl5, station.cal.cl1, station.cal.cl2,
              station.cal.cl3, station.cal.cl4, station.cal.cl5, obs.cl6 = NULL, wt6 = NULL)
```



